A Heuristic Approach towards Drawings of Graphs with High Crossing Resolution \thanks{A preliminary version of this work has appeared in the Proceedings of the 26th International Symposium on Graph Drawing and Network Visualization (GD 2018). This work is supported by the DFG grant Ka812/17-1}

### 2018-09-29 paper/journal.tex
Continue working.

\begin{table*}
\caption{Summary of the results for the Graph Drawing Contest 2017.}
\centering
\begin{tabular}{c|c|c|c|c}
\toprule
~~Graph~~ & ~~CoffeeVM~~ & ~~TuebingenMidnight~~ & ~~Time restricted~~ & ~~Our best~~ \\
\midrule
1 & 90.00  & 77  & 89.99 & 89.99\\
2 & 88.23  & 42  & 88.21 & 88.7 \\
3 & 90.00  & 89  & 87.86 & 89.95 \\
4 & 88.97  & 89  & 77.13 & 89.05 \\
5 & 80.40  & 30  & 78.68 & 86.96 \\
6 & 90.00  & 78  & 89.96 & 89.96\\
7 & 56.53  & 34  & 55.77 & 63.62 \\
8 & 84.95  & 61  & 81.18 & 89.28 \\
9 & 59.88  & 9   & 54.63 & 88.2 \\
10 & 20.97  & 4  & 23.60 & 23.72 \\
11 & 46.68  & 6  & 57.00 & 72.00 \\
12 & 36.47  & 5  & 26.24 & 35.86 \\
13 & 25.45  & 4  & 22.43 & 33.68 \\
14 & 33.52  & 5  & 29.69 & 43.08 \\
15 & 20.51  & 4  & 13.51 & 29.18 \\
16 & 19.83  & 3  & 12.13 & 26.12 \\
\bottomrule
\end{tabular}
\label{tab:gdContest2017}
\end{table*}

@@

% ==================================================================
\subsection{Graph Drawing Contests}
\label{ssec:contest}
% ==================================================================

Every year, the Graph Drawing conference organizes a contest, in which the task is to visualize a set of challenge graphs in a predefined drawing style. The teams participating to the contest receive a set of challenge graphs, and after one hour they must submit their final drawings for each of them. The team with the highest cumulative score wins. In years 2017 and 2018, the task of the contest was the crossing resolution maximization problem, which actually formed our primary motivation for this work.

@@

It is far from clear that the wining team was the team  ``CoffeeVM''. Our team ``TuebingenMidnight''  miserably performed. As already mentioned, each team had only one hour to compute a layout for each of the $16$ challenge graphs. In Table~\ref{tab:gdContest2017}, we additionally provide results that were achieved with our algorithm with the same time limit (see column ``Time restricted''), as well as our best results, which were achieved without any time limitations (see column ``Our best'').

We can observe that for almost all graphs, our new approach achieves only slightly worse results than the ones of the contest's winner when restricted within the one hour. On a few graphs (namely, graphs 10 and 11), we even achieved better results. With a single exception (namely, graph 4), we could easily outperformed our results from last year. If we neglect the time restriction, for all the graphs, the results  are (sometimes considerably) better than or at least about the same as the contest's winner.

%We can conclude that our new approach has good potential for the application in this year's graph drawing contest, however, we also note that more careful graph dependent parameterization will be needed to compute competitive solutions within the provided time.

\myparagraph{Graph Drawing Contest 2018} In 2018,  
\vspace{10cm}

@@

We conclude by noting that our motivation to work with this problem was our participation to the Graph Drawing contest 2017, where we performed miserably using a force-directed algorithm. As our evaluation shows, the performance of such algorithms is good, only when several aesthetic criteria are taken into account; our new approach is definitely better as also evidenced by our experiments. The framework that we developed seems to be quite adaptable to optimize or to take into account also other desired aesthetic properties of a drawing. Thus, as a future direction, we plan to further extend and evaluate our technique, e.g., by using a multi-criteria objective function (i.e., that is not limited to the crossing angles) that takes into account more aesthetic criteria.

>>>>

\begin{table*}
\caption{Summary of the results for the Graph Drawing Contest 2017.}
\centering
\begin{tabular}{c|c|c|c|c}
\toprule
~~Graph~~ & ~~CoffeeVM~~ & ~~TuebingenMidnight~~ & ~~Time restricted~~ & ~~Our best~~ \\
\midrule
1 & 90.00$\circ$   & 77$^\circ$ & 89.99$^\circ$ & 89.99$^\circ$\\
2 & 88.23$^\circ$  & 42$^\circ$ & 88.21$^\circ$ & 88.70$^\circ$\\
3 & 90.00$^\circ$  & 89$^\circ$ & 87.86$^\circ$ & 89.95$^\circ$\\
4 & 88.97$^\circ$  & 89$^\circ$ & 77.13$^\circ$ & 89.05$^\circ$\\
5 & 80.40$^\circ$  & 30$^\circ$ & 78.68$^\circ$ & 86.96$^\circ$\\
6 & 90.00$^\circ$  & 78$^\circ$ & 89.96$^\circ$ & 89.96$^\circ$\\
7 & 56.53$^\circ$  & 34$^\circ$ & 55.77$^\circ$ & 63.62$^\circ$\\
8 & 84.95$^\circ$  & 61$^\circ$ & 81.18$^\circ$ & 89.28$^\circ$\\
9 & 59.88$^\circ$  & 9$^\circ$  & 54.63$^\circ$ & 88.20$^\circ$\\
10 & 20.97$^\circ$ & 4$^\circ$  & 23.60$^\circ$ & 23.72$^\circ$\\
11 & 46.68$^\circ$ & 6$^\circ$  & 57.00$^\circ$ & 72.00$^\circ$\\
12 & 36.47$^\circ$ & 5$^\circ$  & 26.24$^\circ$ & 35.86$^\circ$\\
13 & 25.45$^\circ$ & 4$^\circ$  & 22.43$^\circ$ & 33.68$^\circ$\\
14 & 33.52$^\circ$ & 5$^\circ$  & 29.69$^\circ$ & 43.08$^\circ$\\
15 & 20.51$^\circ$ & 4$^\circ$  & 13.51$^\circ$ & 29.18$^\circ$\\
16 & 19.83$^\circ$ & 3$^\circ$  & 12.13$^\circ$ & 26.12$^\circ$\\
\bottomrule
\end{tabular}
\label{tab:gdContest2017}
\end{table*}

\begin{table*}
\caption{Summary of the results for the Graph Drawing Contest 2018.}
\centering
\begin{tabular}{c|c|c|c}
\toprule
~~Graph~~ & ~~TuebingenColdShower~~ & ~~CoffeeVM+~~ & ~~Our best~~ \\
\midrule
1 & 90.00$\circ$   & 77$^\circ$ & 89.99$^\circ$\\
2 & 88.23$^\circ$  & 42$^\circ$ & 88.70$^\circ$\\
3 & 90.00$^\circ$  & 89$^\circ$ & 89.95$^\circ$\\
4 & 88.97$^\circ$  & 89$^\circ$ & 89.05$^\circ$\\
5 & 80.40$^\circ$  & 30$^\circ$ & 86.96$^\circ$\\
6 & 90.00$^\circ$  & 78$^\circ$ & 89.96$^\circ$\\
7 & 56.53$^\circ$  & 34$^\circ$ & 63.62$^\circ$\\
8 & 84.95$^\circ$  & 61$^\circ$ & 89.28$^\circ$\\
9 & 59.88$^\circ$  & 9$^\circ$  & 88.20$^\circ$\\
10 & 20.97$^\circ$ & 4$^\circ$  & 23.72$^\circ$\\
11 & 46.68$^\circ$ & 6$^\circ$  & 72.00$^\circ$\\
12 & 36.47$^\circ$ & 5$^\circ$  & 35.86$^\circ$\\
13 & 25.45$^\circ$ & 4$^\circ$  & 33.68$^\circ$\\
14 & 33.52$^\circ$ & 5$^\circ$  & 43.08$^\circ$\\
\bottomrule
\end{tabular}
\label{tab:gdContest2018}
\end{table*}

@@

% ==================================================================
\subsection{Graph Drawing Contests 2018 and 2019}
\label{ssec:contest}
% ==================================================================

Every year, the Graph Drawing conference organizes a contest, in which the task is to visualize a set of challenge graphs in a predefined drawing style. The teams participating to the contest receive a set of challenge graphs, and after one hour they must submit their final drawings for each of them. The team with the highest cumulative score wins. In years 2017 and 2018, the task of the contest was to produce a drawing for each of the given challenge graphs with as high crossing resolution as possible (which actually also formed our primary motivation for this work).

@@

It is far from clear that the wining team was the team  ``\texttt{CoffeeVM}''. Our team ``\texttt{TuebingenMidnight}''  miserably performed; we actually took the third position out of a total of four teams that participated. As already mentioned, each team had only one hour to compute a layout for each of the challenge graphs, which in year 2017 were in total $16$. In Table~\ref{tab:gdContest2017}, we additionally provide results that were achieved by the algorithm presented in this paper in two settings; within the time limit of the contest (see column ``Time restricted''), as well as our best results, which were achieved without any time limitations (see column ``Our best'').

We can observe that for almost all graphs, our new approach achieves only slightly worse results than the ones of the contest's winner when restricted within the one hour. On a few graphs (namely, graphs 10 and 11), we even achieved better results. With a single exception (namely, graph 4), we could easily outperform the results that we achieved with the spring-embedder algorithm. If we neglect the time restriction, then for all the graphs, the results  are (sometimes considerably) better than or at least about the same as the contest's winner.

\myparagraph{Graph Drawing Contest 2018} In 2018, we participated again to the Graph Drawing contest under the name ``\texttt{T\"ubingenColdShower}'' (using an implementation of the algorithm presented in this paper). The winning team of the Graph Drawing contest 2017 also participated under the name ``\texttt{CoffeeVM+}''. Table~\ref{tab:gdContest2018} summarizes the results, which are also available at \texttt{www.graphdrawing.de/contest2018/results.html}.

It is eye-catching that our team was the winning one; team \texttt{CoffeeVM+} took the second position of the contest (out of a total of four teams that participated to the contest). It is worth noting that for almost all $14$ challenge graphs our team achieved significantly better results than those of the second team \texttt{CoffeeVM+}, which clearly indicates that our new approach is very competitive (and definitely better than our previous,  as also evidenced by the experimental evaluation).

@@

We conclude by noting that our motivation to work with this problem was our participation to the Graph Drawing contest 2017, where we performed miserably using a force-directed algorithm. As our evaluation shows, the performance of such algorithms is good, only when several aesthetic criteria are taken into account.

The framework that we developed seems to be quite adaptable to optimize or to take into account also other desired aesthetic properties of a drawing. Thus, as a future direction, we plan to further extend and evaluate our technique, e.g., by using a multi-criteria objective function (i.e., that is not limited to the crossing angles) that takes into account more aesthetic criteria.
